---
title: "Activity 3 - Day 1"
output: github_document
---


# Day 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(GGally)
```

```{r data, include=FALSE}
hfi <- readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")
```

## Task 3: Load the data

This is an observational study.

```{r histogram}
pf_hist<-ggplot(data = hfi, aes(x = pf_score)) +
  geom_histogram(binwidth = 0.25) +
  xlab("pf_score")
```

The distribution is skewed to the right, meaning that the majority of countries have a high pf_score. There are 3 peaks. This is not what I expected to see, since I figured it would be normally distributed.

## Year and homicide rates in Mexico
```{r year_homicide}
hfi_mex <-hfi %>% filter(countries=="Mexico")
year_homicide_mex <- ggplot(hfi_mex) + 
    geom_bar(aes(x = year, y = pf_ss_homicide), stat = 'identity')
```
The homicide rate appears to be decreasing.

## Task 4: Pairwise relationships

$$
\texttt{pf\\_score} = \beta_0 + \beta_1 \times \texttt{pf\\_expression\\_control} + \varepsilon
$$
#Come back to questions

```{r pair_scores}
hfi %>% 
  select(ends_with("_score")) %>% 
  ggpairs()
```

$$
\texttt{pf\\_score} = \beta_0 + \beta_1 \times \texttt{hf\\_score} + \beta_2 \times \texttt{ef\\_score} + \varepsilon
$$
```{r mult_lin_model}
m_hr_ef <- lm(pf_score ~ hf_score + ef_score, data = hfi)
  tidy(m_hr_ef)
```

$$
\hat{y} = 2 \times \texttt{hf\\_score} - \texttt{ef\\_score}
$$
Come back for question

# Day 2

```{r}

```






